---
title: "Multilayer perceptron with RSNNS package using fold sampling"
author: "David Banh - AskExplain"
date: "04/01/2022"
output: pdf_document
---


# Multilayer perceptron Regression using sample summaries runs faster, retains accuracy

#### Summarising or Folding the samples is a way of reducing the total number of samples to a manageable number in order to run prediction algorithms on modern day machines. The folded samples are then unfolded to predict the full dataset.

#### A way to fold the total number of samples while retaining the original sample structure is done via Generative Encoding (gcode): https://github.com/AskExplain/gcode/tree/alpha_test_v2022.1


```{r fold_sampling, fig.show="hide", results="hide", message = FALSE, warning = FALSE, }

# Removes one feature at a time and uses it as the variable to be predicted (y variable)



# Total permutations :

permutation_test_number <- 10





# Run SVD decomposition of samples to a reduced sample space

source("./decompose_sample_space.R")


# Run gcode encoding of samples to a reduced sample space

source("./encode_sample_space.R")






```




### Boxplots of mean absolute error and runtime are plotted for every unique run of the neural network regression via RSNNS package. 

#### Of great importance, the runtime does not include the running of the SVD or gcode algorithms.

```{r Boxplots of total mean absolute error and runtime, fig.height = 5}

# Mean Absolute Error


boxplot(data.frame(gcode = (total_mae.gcode),
                   svd = (total_mae.svd),
                   mlp1 = (total_mae.lreg.1),
                   mlp2 = (total_mae.lreg.2)), 
        outline = F,
        horizontal = T, 
        main = "Mean Absolute Error distribution")







# Runtime








boxplot(data.frame(gcode = total_time.gcode,
                   svd = total_time.svd,
                   mlp1 = total_time.lreg.1,
                   mlp2 = total_time.lreg.2), 
        outline = F,
        horizontal = T, 
        main = "Runtime distribution")

```





